Constrain the Merger History of Primordial-Black-Hole Binaries from GWTC-3

### 2022-10-31 latex/paper.tex
update
Updates from Overleaf

Besides the astrophysical black holes, another possible explanation for the LVK BBHs is the primordial black holes (PBHs) \cite{Bird:2016dcv,Sasaki:2016jop,Chen:2018czv,Liu:2018ess,Chen:2021nxo}. 
PBHs are black holes formed in the very early Universe through the gravitational collapse of the primordial density fluctuations \cite{Hawking:1971ei,Carr:1974nx}. Recently, PBHs have attracted considerable attention \cite{Garcia-Bellido:2017mdw,Carr:2017jsz,Germani:2017bcs,Liu:2019rnx,Cai:2019elf,Cai:2019bmk,DeLuca:2020sae,Vaskonen:2020lbd,DeLuca:2020agl,Hutsi:2020sol,Sasaki:2018dmp,Carr:2020gox,Carr:2020xqk,Liu:2021jnw} because they can be not only the sources of LVK detections~\cite{Bird:2016dcv,Sasaki:2016jop}, but also candidates of cold dark matter (CDM) \cite{Carr:2016drx} and the seeds for galaxy formation~\cite{Bean:2002kx,Kawasaki:2012kn}. The formation of PBHs would inevitably accompany the production of scalar-induced GWs \cite{Saito:2008jc,Yuan:2019udt,Yuan:2019wwo,Yuan:2019fwv,Chen:2019xse,DeLuca:2019ufz,Bartolo:2018rku,Bartolo:2018evs}.
%PBHs can also be natural candidates of cold dark matter (CDM). 
Recent studies \cite{Chen:2021nxo,Chen:2022fda} show that the BBHs from GWTC-3 are consistent with the PBH scenario, and the abundance of PBH in CDM, $\fpbh$, should be in the order of $\mathcal{O}(10^{-3})$ to explain LVK BBHs. In particular, the merger rate for GW190521 derived from the PBH model is consistent with that inferred by LVK, indicating that GW190521 can be a PBH binary \cite{DeLuca:2020sae,Chen:2021nxo}.

>>>>

Besides the astrophysical black holes, another possible explanation for the LVK BBHs is the primordial black holes (PBHs) \cite{Bird:2016dcv,Sasaki:2016jop,Chen:2018czv,Liu:2018ess,Chen:2021nxo}. 
PBHs are black holes formed in the very early Universe through the gravitational collapse of the primordial density fluctuations \cite{Hawking:1971ei,Carr:1974nx}. Recently, PBHs have attracted considerable attention \cite{Garcia-Bellido:2017mdw,Carr:2017jsz,Germani:2017bcs,Liu:2019rnx,Cai:2019elf,Cai:2019bmk,DeLuca:2020sae,Vaskonen:2020lbd,DeLuca:2020agl,Hutsi:2020sol,Sasaki:2018dmp,Carr:2020gox,Carr:2020xqk,Liu:2021jnw,Wang:2022nml} because they can be not only the sources of LVK detections~\cite{Bird:2016dcv,Sasaki:2016jop}, but also candidates of cold dark matter (CDM) \cite{Carr:2016drx} and the seeds for galaxy formation~\cite{Bean:2002kx,Kawasaki:2012kn}. The formation of PBHs would inevitably accompany the production of scalar-induced GWs \cite{Saito:2008jc,Yuan:2019udt,Yuan:2019wwo,Yuan:2019fwv,Chen:2019xse,DeLuca:2019ufz,Bartolo:2018rku,Bartolo:2018evs}.
%PBHs can also be natural candidates of cold dark matter (CDM). 
Recent studies \cite{Chen:2021nxo,Chen:2022fda} show that the BBHs from GWTC-3 are consistent with the PBH scenario, and the abundance of PBH in CDM, $\fpbh$, should be in the order of $\mathcal{O}(10^{-3})$ to explain LVK BBHs. In particular, the merger rate for GW190521 derived from the PBH model is consistent with that inferred by LVK, indicating that GW190521 can be a PBH binary \cite{DeLuca:2020sae,Chen:2021nxo}.
